\section{Problem Statement}

\begin{enumerate}
  \item \textbf{Manual Monitoring is Impractical}: Cryptocurrency markets operate 24/7 with high volatility. For retail traders, manually tracking and mirroring the trades of professional "alpha" wallets is physically impossible without automated tools, leading to missed opportunities and suboptimal entry prices.
  \item \textbf{Custodial Risk in Centralized Platforms}: Traditional copy-trading platforms (e.g., eToro, Bybit) require users to deposit funds into centralized exchange wallets. This exposes users to counterparty risks, insolvency events (e.g., FTX), and potential withdrawal freezes.
  \item \textbf{Key-Sharing Risks in Botting}: Existing on-chain automation tools often require users to export their private keys or API keys to third-party servers. This creates a massive security vulnerability, where a single server breach could result in total loss of user funds.
  \item \textbf{High Costs on EVM Chains}: Ethereum-based solutions suffer from high gas fees and slow finality. This makes high-frequency copy-trading prohibitively expensive for smaller portfolios, as transaction costs erode potential profits.
  \item \textbf{Lack of Trustless Standards}: There is currently no standardized, trustless protocol for on-chain copy trading that guarantees execution transparency without relying on opaque off-chain logic or custodial bridges.
  \item \textbf{Convergent Mirroring and Liquidity Crushing}: Naive wallet mirroring protocols typically copy raw token amounts or fixed percentages without regard for the follower's relative liquidity or the trader's total conviction. When multiple followers attempt to mirror a single high-signal trade simultaneously, they create an artificial demand spike that ``crushes'' available liquidity, resulting in massive slippage for the followers and eroding the original strategy's alpha.
\end{enumerate}
